---
title: "DataGuide_Lesson1"
output: html_document
author: Milos Janicki
---


Task:  
1.Load in the mtcars dataset.  
2.Use the exploratory functions you learned today to get an initial view.  
3. Do histograms of the variables - are they normally distributed? Feel free to play around with the function parameters, to make the plots more beautiful. Hint: check the documentation of the function to check what parameters you can control.  
4.Plot several plots next to each other.  
5.Do the shapiro test to make sure what you see is right.  


## 1.Load in the mtcars dataset.

```{r}
library(datasets)
data(mtcars)
```

## 2. Use the exploratory functions you learned today to get an initial view.

```{r}
head(mtcars)
summary(mtcars)
str(mtcars)
```


## 3. Do histograms of the variables - are they normally distributed? Feel free to play around with the function parameters, to make the plots more beautiful. Hint: check the documentation of the function to check what parameters you can control.
## 4.Plot several plots next to each other.
## 5.Do the shapiro test to make sure what you see is right.

```{r}
par(mar=c(1,1,1,1)+0)

attach(mtcars)
par(mfrow=c(2,3), mai = c(1, 0.1, 0.1, 0.1))
hist(mpg)
hist(cyl)
hist(disp)
qqnorm(mpg); qqline(mpg, col = 2)
qqnorm(cyl); qqline(cyl, col = 2)
qqnorm(disp); qqline(disp, col = 2)
shapiro.test(mpg)
shapiro.test(cyl)
shapiro.test(disp)
par(mfrow=c(2,3))
hist(hp)
hist(drat)
hist(wt)
qqnorm(hp); qqline(hp, col = 2)
qqnorm(drat); qqline(drat, col = 2)
qqnorm(wt); qqline(wt, col = 2)
shapiro.test(hp)
shapiro.test(drat)
shapiro.test(wt)
par(mfrow=c(2,3), mai = c(1, 0.1, 0.1, 0.1))
hist(qsec)
hist(vs)
hist(am)
qqnorm(qsec); qqline(qsec, col = 2)
qqnorm(vs); qqline(vs, col = 2)
qqnorm(am); qqline(am, col = 2)
shapiro.test(qsec)
shapiro.test(vs)
shapiro.test(am)
par(mfrow=c(2,2))
hist(carb)
qqnorm(carb);qqline(carb,col=2)
hist(gear)
qqnorm(gear); qqline(gear, col = 2)
shapiro.test(carb)
shapiro.test(gear)
```

```{r}
attach(mtcars)
par(mfrow=c(2,2), mai = c(1, 0.1, 0.1, 0.1))
plot(wt,mpg)
plot(wt,qsec)
plot(drat,wt)
```



##Conclusions:
Variables 'disp' and 'hp' are not normally distributed since the p-value of Shapiro's test is lower than 0,05
We can assume that other variables tested in this example are normally distributed

