---
title: "DateGuide_Lesson2"
author: "Milos Janicki"
date: "9 November 2016"
output: html_document
---

Task:  

Now it is your turn. Use what you have learned from the iris dataset on a new one. The dataset is uploaded as a csv file on the following URL:  http://goo.gl/HKnl74. This is simulated data from an amusement park. For this exercise, make sure to write the report in an rmarkdown format for nicer presentation and sharing.


Load data
```{r}
setwd('/Users/milosjanicki/Data_projects/Date_Guide/')
apd <- read.csv('2.csv')
```

First Glance EDA
```{r}
summary(apd)
str(apd)
```

Histograms, Corellation and Shapiro-Test for all variables
```{r}
par(mar=c(1,1,1,1)+0)

attach(apd)
par(mfrow=c(2,3), mai = c(1, 0.1, 0.1, 0.1))
hist(num.child)
hist(distance)
hist(rides)
qqnorm(num.child); qqline(num.child, col = 2)
qqnorm(distance); qqline(distance, col = 2)
qqnorm(rides); qqline(rides,col=2)
shapiro.test(rides)
shapiro.test(num.child)
shapiro.test(distance)
par(mfrow=c(2,3), mai = c(1, 0.1, 0.1, 0.1))
hist(games)
hist(wait)
hist(clean)
qqnorm(games); qqline(games, col = 2)
qqnorm(wait); qqline(wait, col = 2)
qqnorm(clean); qqline(clean,col=2)
shapiro.test(games)
shapiro.test(wait)
shapiro.test(clean)
hist(overall)
qqnorm(overall); qqline(overall, col = 2)
shapiro.test(overall)

par(mfrow=c(1,1))
boxplot(apd[,3:8])

pairs(apd)

library(GGally)
ggpairs(apd)



```


